### 2016-01-18 paper.tex
Tighten up and expand last paragraph of introduction

The present task was to acquire a new dataset for the lower solidity RM2
turbine, but at higher Reynolds numbers than those achieved in the experiments
at SAFL. It was suspected that the strut drag model in CACTUS could be the
source of some discrepancy. Thus, the strut drag was deliberately and
significantly increased in the physical model to provide data to help answer
that question. This dataset is publicly available for both validation of CACTUS
and other numerical models \cite{Bachant2015-RM2-data}.

>>>>

The present task was to acquire a new experimental dataset for the lower
solidity RM2 turbine at sufficient Reynolds numbers to be relevant to full-scale
modeling. It was hypothesized that the parasitic losses from rotor blade support
struts could play an important role in overall turbine performance. Thus, the
parasitic torque from strut drag was measured without blades, then deliberately
and significantly increased in the physical model to provide data to help answer
that question. The velocity field in the near-wake of the turbine was then
measured to compare with measurements from a higher solidity rotor in the same
experimental setup \cite{Bachant2015-JoT}, and provide validation data for
numerical models that predict wake flows, which determine turbine--turbine
interaction and optimal spacing for turbine arrays. This dataset, along with the
code for processing and visualization, is publicly available
\cite{Bachant2015-RM2-data}.
